\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Logbook 1\vspace{-5mm}

### 2023-11-30 text/LogBooks/logbook1.tex
logbook 1

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Investigation Proposal\vspace{-5mm}}
\date{November 2023}

@@

\begin{multicols}{2}

% \tableofcontents

\section{Proposal Summary}

State clearly the aim of the proposed experiment together with the general and specific scientific background.

\section{Experimental technique}

Describe the experimental set-up and requirements. Queries concerning the feasibility (technical or safety aspects) of an experiment should be clarified with hosts before the proposal is submitted.

\section{Safety considerations}

Experimental conditions requiring special safety precautions such as the use of lasers, high pressure cells, bacteria, dangerous substances, toxic substances and radioactive materials, must be identified in the proposal.

\section{Beamtime requested}

Specify the dates of the beamtime requested and the number of shifts. The beamtime requested should be in accordance with the estimated duration of the experiment. Specify the place and the investigators who will guide the experiment.

\section{Results expected}

Describe the results expected from the measurements, their scientific (or technical) relevance, and how they relate to existing work on the topic.

\section{Concluding remarks}

Justify the beam time you request and give technical reasons which make the apparatus necessary for your experiment. Include REFERENCES where these are relevant, but do not assume that they will be systematically consulted for essential details.

\printbibliography
\nocite{*}

\end{multicols}

>>>>

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Logbook 1\vspace{-5mm}}
\date{30 November 2023}

@@

% \begin{multicols}{2}

\vspace*{1cm}

On the 30\textsuperscript{th} of November, the four members of our group went to the second meeting with professors Rodrigo Mateus, Rui \_\_ and Norberto \_\_ at CTN Loures. Our goal was to discuss the work we will be doing in the following session at the same laboratory.
We arrived at 9:30 AM and started discussing the questions that we had been requested to answer the previous session.

\paragraph*{}

The professors turned on the accelerator and went through the different components of its layout and experiment setup. We focused on the detector part and we were able to see both the samples and the silicon detectors next to it.

\paragraph*{}

The rest of the session was followed by a discussion about multiple theoretical and experimental aspects of the project. We discussed the following topics:

\begin{enumerate}
  \item The structure of the tandem 2.5 MeV accelerator and both it's acceleration tubes. They allow the proton beam to reach the target with a kinetic energy of 5 MeV instead of 2.5 MeV (only one tube);
  \item The radiation at the laboratory - we were told that the radiation levels are very low unless we were very close to the accelerator.
  \item The vacuum inside the tubes - we estimated that, at a pressure of $10^{-7}$ mbar (the pressure inside the tubes), there are approximately $10^9$ particles per cubic centimeter. This is a good vacuum meaning that the protons won't collide with other particles and will be able to reach the target without losing energy;
  \item The equation that we aim to study: a proton collides with $^7$Li and produces $^8$Be, which then decays into two alpha particles. The decay process is not detectable, so we will only be able to detect the alpha particles:

  \begin{equation}
    \ce{^7Li + ^1H -> ^8Be -> 2\alpha}
  \end{equation}

  \item The importance of the electromagnets used to deviate the trajectory of the proton beam. We understood that deflection angle is related to the mass and charge of the particle, therefore different particles will have different trajectories, meaning we can isolate the protons on the incident beam;
  \item Samples used: in the next session, we are going to work with need to collect the radiation spectrum of two different Lithium-7 samples: one of them is glass sample composed of silicon, boron and lithium and the other one is a implant sample, which is a thin layer of lithium implanted in a silicon substrate;
  \item Finally, we discussed the expected results for both samples - phenomena such as Rutherford Backscattering, Elastic Scattering and profile of the energy spectrum of the alpha particles were mentioned.
\end{enumerate}

We left the laboratory at 12:00 PM.

% \end{multicols}
